---
title: "Backtest"
author: "https://minchun.shinyapps.io/backtest/"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Input                                 | Value
--------------------------------      | ----------------------------------------
Stock                                 | `r input$test_stock`
Benchmark                             | `r input$test_target`
Analysis Date range                   | `r input$test_dates[1]`  ~ `r input$test_dates[2]`
Plot 1 Scale                          | `r input$test_scale_plot1`
Transformation                        | `r input$test_transform`
Open                                  | `r input$test_direction` 
Stoploss(%)                           | `r input$stoploss`    
Index1                                | `r input$test_index`
Differentiation                       | `r input$test_differential`
Strategy using Criteria2              | `r input$test_diff_index_strategy`
Based on                              | `r input$test_useIndex1`
Index2                                | `r input$test_diff_index`
Index Scale                           | `r input$test_indexscale`
Index Threhold                        | `r input$test_num`
Open Consective Threhold              | `r input$test_open`
Close Consective Threhold             | `r input$test_close`

```{r backtest, echo=FALSE}
tradedata <- plot_backtest(input)
tradedata$plot_backtest
```

```{r pressure, echo=FALSE}
kable(table_tradinganalyse(tradedata, input)) 
```
